---
title: "afblue"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  github_document:
    toc: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "readme-figs/"
)
```


This is an R-package that makes it easy to compute the BLUE for estimating 
allele frequency amongst the founders given the pedigree connecting a sample.

It also provides an algorithm for determining optimal sibling removal schemes
and it makes it easy to compute effective sample sizes.

## Installing the package

You can get the package thus:
```{r, eval=FALSE}
devtools::install_github("eriqande/afblue")
```

Because `devtools::install_github` might not recursively install dependencies
you might need or want to also do this:
```{r, eval=FALSE}
install.packages(c("dplyr", "kinship2", "magrittr", "stringr", "tidyr"))
```

## Reproducing the simulations of Waples and Anderson

If you want to see how the package was used in 
the paper "Purging putative siblings from population genetic datasets: A cautionary view"  by Robin S. Waples
and Eric C. Anderson in _Molecular Ecology_ then, after you have done the above line,
you should get the whole
repository which includes the scripts.  Do it like this on your command line.
```{sh, eval=FALSE} 
git clone https://github.com/eriqande/afblue
```
Or just get the package from Dryad.

Then open up the Rstudio project (`afblue.Rproj`) in that repository.


### Main paper simulations
In order to rerun the simulations done in the paper you must run the code in the files
`R-Robin/ESS.R` and `R-Robin/Sims.R`.  


### Coho salmon population investigations
In order to rerun the analyses on the 
coho salmon populations
you may need to install some more packages if you do not
already have them:
```{r, eval=FALSE}
install.packages(c("readr", "ggplot2", "grid", "gridExtra", "forcats"))
```
Then, armed with those packages, you must run the code in  
`./R-main/coho-afblue-analysis.R` with the working directory being the top level of the 
repository/Rstudio project.  

Running that script will produce a directory called `outputs` and will fill it with the following 
output files:
```
as-if-true-pedigrees.pdf
coho_summ_table-related.csv
coho_summ_table-unrelated.csv
ess_fig_a.pdf
ess_fig_b.pdf
full_blue_results.csv
unrelateds-with-spuriously-inferred-pedigrees.pdf
```
which are various plots and outputs that appear in the paper.
